Community Analysis

### 2022-04-09 R/08-community.Rmd
Trying to update community analysis to work smoothly

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir=normalizePath('../'))

@@

```{r initialize_packages}
library(tidyverse)
library(phyloseq)
library(decontam)
library(microViz)
library(knitr)
library(corncob)
library(DivNet)
library(magrittr)
library(vegan)
library(ggpubr)
library(SpiecEasi)
library(ggthemes)
library(broom)

@@

```{r ggplot-settings}
```

@@

ord_calc_jacc <-
  ps_fixed %>%
  dist_calc("jaccard", binary = TRUE) %>%
  ord_calc(method = "NMDS")

@@

jacc <- 
  ord_calc_jacc %>% 
  ord_plot(color = "treat") +
  theme_tufte() +
  geom_rangeframe() +
  coord_cartesian(clip="off") +
  scale_color_manual(name = "Treatment", 
                       labels = c('Neutral', 'Positive'),
                       values = c('gray40', 'darkorange2'))

@@

@@

```{r}
library(ALDEx2)
data(selex)
#subset only the last 400 features for efficiency
selex.sub <- selex[1:400,]
conds <- c(rep("NS", 7), rep("S", 7))
x <- aldex.clr(selex.sub, conds, mc.samples=16, denom="iqlr", verbose=F)
x.tt <- aldex.ttest(x, paired.test=FALSE, verbose=FALSE)
x.effect <- aldex.effect(x, CI=T, verbose=FALSE)
head(x.effect)

@@

```{r}
ps_fixed_family <- speedyseq::tax_glom(ps_fixed, taxrank="Family")

@@

```{r corncob_treatment, fig.hight=40}
ps_fixed_family <- speedyseq::tax_glom(ps_fixed, taxrank="Family")

@@

```{r}
biom_file <- "Output/func_table_from_biom_json.biom"

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = TRUE)
knitr::opts_knit$set(root.dir=normalizePath('../'))

@@

```{r initialize_packages}
library(tidyverse)
library(phyloseq)
library(decontam)
library(microViz)
library(knitr)
library(corncob)
library(DivNet)
library(magrittr)
library(vegan)
library(ggpubr)
# library(SpiecEasi)
library(ggthemes)
library(broom)

@@

@@

ord_calc_jacc <-
  ps_fixed %>%
  dist_calc("jaccard", binary = TRUE) %>%
  ord_calc(method = "PCoA")

@@

jacc <- 
  ord_calc_jacc %>% 
  ord_plot(color = "treat") +
  theme_tufte() +
  geom_rangeframe() +
  coord_fixed(3.9/48.3) +
  # coord_cartesian(clip="off") +
  scale_color_manual(name = "Treatment", 
                       labels = c('Neutral', 'Positive'),
                       values = c('gray40', 'darkorange2'))

@@

```{r corncob_treatment, results=FALSE, fig.hight=40}
ps_fixed_family <- speedyseq::tax_glom(ps_fixed, taxrank="Family")

```{r stahp}
knitr::opts_chunk$set(eval = FALSE)

@@

```{r, eval = FALSE}
library(ALDEx2)
data(selex)
#subset only the last 400 features for efficiency
selex.sub <- selex[1:400,]
conds <- c(rep("NS", 7), rep("S", 7))
x <- aldex.clr(selex.sub, conds, mc.samples=16, denom="iqlr", verbose=F)
x.tt <- aldex.ttest(x, paired.test=FALSE, verbose=FALSE)
x.effect <- aldex.effect(x, CI=T, verbose=FALSE)
head(x.effect)

@@

```{r, eval=FALSE}
ps_fixed_family <- speedyseq::tax_glom(ps_fixed, taxrank="Family")

@@

@@

```{r, eval=FALSE}
biom_file <- "Output/func_table_from_biom_json.biom"
